---
title: "Homework: Packages, Scripts, Documents, and Functions"
author: "Oliver Titus"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits = 3)
```

```{r load-sas-libraries, echo = F, message = F, warning = F}
saspath <- "C:/Program Files/SASHome/SASFoundation/9.4/sas.exe" # Your SAS path goes here
sasopts <- "-nosplash -ls 75"

# Please leave this in so that I can test it!
# saspath <- "/usr/local/SASHome/SASFoundation/9.4/bin/sas_en" 
# sasopts <- "-ls 75"
knitr::opts_chunk$set(engine.path=list(sas=saspath, saslog=saspath, sashtml=saspath),
                      engine.opts=list(sas=sasopts, saslog=sasopts, sashtml=sasopts), 
                      comment=NA)
library(SASmarkdown)
```

## Instructions
This homework has two main problems. In the FizzBuzz section, you should only modify the code chunks. In the Packages/Procedures section, you should modify the text (anything that doesn't have a `###` in front of it) and the code chunks. Feel free to add additional code chunks as necessary.

Make sure you also edit the author name at the top of the document. 

When you are finished with the assignment: 

1. Save the file as 03_Lastname_Firstname.Rmd and compile it
2. Commit the Rmd file and corresponding html file to your homework git repo
3. Push the commit to github
4. Locate the Rmd file on github and click on the SHA link for the file
5. Paste the url of the resulting page into Canvas to submit your assignment.

Your assignment must compile on a different computer as long as the saspath is set correctly for that machine.

## FizzBuzz Functions

The "FizzBuzz Test" is a famous programming interview question. 
> Write a program that prints the numbers from 1 to 30. But for multiples of three print “Fizz” instead of the number and for the multiples of five print “Buzz”. For numbers which are multiples of both three and five print “FizzBuzz

In the R chunk below, write a function which will solve this problem. Do not change the function name or parameter name. 

Show the results from running your function on the integers 1-20, as well as a sequence of 10 random integers between 0 and 100. (This code is already written for you).

```{r fizzbuzz-solution, echo = T}
fizzbuzz <- function(x) {
  
  for(x in x) {
  
  if (x %% 15 == 0) {
    print("FizzBuzz")
  }
  
  else if (x %% 5 == 0){
    print("Buzz")
 }
  else if (x %% 3 == 0){
    print("Fizz")
  }
  else {
    print(x)
  } 
}
 }
```

```{r test-fizzbuzz}
fizzbuzz(1:20)
fizzbuzz(sample(1:100, 10)) # sample 10 values from 1 to 100
```

In the sas chunk, write similar code which will solve this problem.

```{r fizzbuzz-sas, engine="sashtml", engine.path=saspath, engine.opts=sasopts, error = T}
proc printto log="saslog.log" new;

proc iml;
start fizzbuzz(x);
  y="";
    if mod(x,15)=0 then y=y+"FizzBuzz";
    if mod(x,5)=0 then y=y+"Buzz";
    if mod(x,3)=0 then y=y+"Fizz";
    return y;
  finish;

x1 = repeat(0, 20); /* initialize x1 */
fb1 = repeat("        ", 20);
do i = 1 to 20;
  x1[i] = i;
  fb1[i] = fizzbuzz(x1[i]);
end;

x2 = repeat(0, 10); /* initialize x2 */
fb2 = repeat("xxxxxxxx", 10); /* initialize fb2 */
do i = 1 to 10;
  x2[i] = rand("Integer", 1, 100);
  fb2[i] = fizzbuzz(x2[i]);
end;

print x1 fb1, x2 fb2;

quit;
```

```{r readlog}
cat(readLines("saslog.log"), sep="\n")
```


```{r cleanuplog}
# Do not forget to remove the log file when you are done!
unlink("saslog.log")
```


## Exploring Packages and Modules

### R Package: ggplot2
#The package I am demonstrating is ggplot2 which is part of the Tidyverse collection of packages. GGplot2 is useful for creating graphics based visualizations of data. Since I don't have a dataset, I just plotted the standard normal distribution below with mean 0 and standard devition 1. 

```{r, cache = T}
library(tidyverse)
ggplot(data.frame(x=c(-4,4)), aes(x=x)) + stat_function(fun=function(x) dnorm(x, mean=0, sd=1))
```
 


### SAS Procedure: PROC SGPLOT

I'm demonstrating the 'sgpolot' procedure here. I chose this since I used the plotting package in R 'ggplot2' and I wanted to explore what package was similar in SAS. Here, I create a dataset for an F distribution with numerator degrees of freedom of 5 and a denominator degrees of freedom of 2. This disribution is plotted below: 

Fill in your code in the chunk below.
```{r proc-demo, engine="sashtml", engine.path=saspath, engine.opts=sasopts, error = T}
proc printto log="saslog.log" new;

data fdist;
  do x = 0 to 5 by .001;
    fdist = pdf("F", x, 5, 2);
    output;
  end;
run;

proc sgplot data=fdist;
  series x = x y = fdist;
run;
```
